Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-12-20 methods.tex
autores

\section{Methods and working hypotheses}\label{S_methods}
%{{{

@@

There is no a temporal window for the model, i.e., the simulation
starts when the process is already stable, and ends before any
galactic effect could modify or affect of fixed variables.
%
The probability for the rise of a MPL is homogeneous over the GHZ.
%
Although the Galaxy has a well known spiral structure, the assumed
sparcity of civilizations makes this assumption very reasonably.
%
Otherwise, if the distribution of civilizations is not sparce, it
could be the case that the spiral arms would host most of the
civilizations, and contacts are frecuent between closely located
civilizations.
%
In such a case we could expect that the interpretation of our results
could be considered as pesimist for the stablishment of a contact with
our planet.
%
We also limit the posibilities of life or other types of civilizations
to the hypothesis usually stated for the definition of the GHZ
\citep{dayal_habitability_2016,gonzalez_galactic_2001,lineweaver_galactic_2004,gonzalez_habitable_2005,morrison_extending_2015,haqq-misra_evolution_2019,rahvar_cosmic_2016,gobat_evolution_2016,
rahvar_cosmic_2016}.
%
\citet{vukotic_astrobiological_2012} propose probabilistic cellular
automata model to explain the astrobiological history of the Milky
Way.
%
This means that we set aside possible civilizations that could survive
in severe conditions or unstable systems, which would prevent the
appeareance of life as we know it.

@@

The exponential distribution of lifespan and waiting times is
justified by considering that the process of appeareance of life in
the galaxy is homogeneous and stationary.
%
This means that there is no preferred location within the GHZ for the
spontaneos appeareance of life, and that the emergence of a
civilization is independent of the existence of previous civilizations 
in the galaxy.
%            
This is equivalent to proposing a Poisson process for the emergence of
MPLs, since there is a close relation between the number of events in
time or space and the waiting time or separation, respectively.
%
That is, these are two alternative approaches to describing the same
process, a Poisson distribution for the number of events implies an
exponential distribution for their sepations, and viceversa.
%
It should be emphasized that the exponential laws used in this work
are assumed, although instead of analyzing results from a particular
parameter chosen ad--hoc, we explore the hypothesis space and analyze
the impact of the values of these parameters on the results.
%

@@

\begin{figure*} % 2D color plot
   \centering
   \includegraphics[width=\textwidth]{matrix_1.pdf}
   \usecaption{F_never_contact}
   \label{F_never_contact}
\end{figure*}

\begin{figure*} % 2D color plot
   \centering
   \includegraphics[width=\textwidth]{matrix_2.pdf}
   \usecaption{F_C_at_A}
   \label{F_C_at_A}
\end{figure*}

@@

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{waiting_s+a_dif_ylog.pdf}
   \usecaption{F_waiting_for_1C}
   \label{F_waiting_for_1C}
\end{figure}

>>>>

%%% S E C T I O N - - - - - - - - - - - - - - - - - - - - - - -
\section{Methods and working hypotheses}\label{S_methods}
%{{{

@@

There is no a temporal window for the model, i.e., the simulation
starts when the process is already stable, and ends before any
galactic effect could modify or affect of fixed variables.
%
The probability for the rise of a MPL is homogeneous over the GHZ.
%
Although the Galaxy has a well known spiral structure, the assumed
sparcity of civilizations makes this assumption very reasonably.
%
Otherwise, if the distribution of civilizations is not sparce, it
could be the case that the spiral arms would host most of the
civilizations, and contacts are frecuent between closely located
civilizations.
%
In such a case we could expect that the interpretation of our results
could be considered as pesimist for the stablishment of a contact with
our planet.
%
We also limit the posibilities of life or other types of civilizations
to the hypothesis usually stated for the definition of the GHZ
\citep{dayal_habitability_2016, gonzalez_galactic_2001,
lineweaver_galactic_2004, gonzalez_habitable_2005,
morrison_extending_2015, haqq-misra_evolution_2019,
rahvar_cosmic_2016, gobat_evolution_2016, rahvar_cosmic_2016}.
%
\citet{vukotic_astrobiological_2012} propose probabilistic cellular
automata model to explain the astrobiological history of the Milky
Way.
%
This means that we set aside possible civilizations that could survive
in severe conditions or unstable systems, which would prevent the
appeareance of life as we know it.

@@

The exponential distribution of lifespan and waiting times is
justified by considering that the process of appeareance of life in
the galaxy is homogeneous and stationary.
%
This means that there is no preferred location within the GHZ for the
spontaneos appeareance of life, and that the emergence of a
civilization is independent of the existence of previous civilizations
in the galaxy.
%            
This is equivalent to proposing a Poisson process for the emergence of
MPLs, since there is a close relation between the number of events in
time or space and the waiting time or separation, respectively.
%
That is, these are two alternative approaches to describing the same
process, a Poisson distribution for the number of events implies an
exponential distribution for their sepations, and viceversa.
%
It should be emphasized that the exponential laws used in this work
are assumed, although instead of analyzing results from a particular
parameter chosen ad--hoc, we explore the hypothesis space and analyze
the impact of the values of these parameters on the results.

@@

@@
